Covariate analysis of HBCC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (DLPFC with CQN normlaisation)

### 2018-07-25 code/Rmd/HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd
Modified model selection markdown for HBCC DLPFC analysis to account for metadata (individual id) changes

knit2synapse::knitToFolderEntity(file = "./HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd",
                                 parentId ="syn9846623",
                                 entityName = 'HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN (Model Selection)')
```

@@

## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)

library(ggplot2)
library(limma)
library(psych)
library(edgeR)
library(cqn)
library(lme4)
library(biomaRt)

@@

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='CMC')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
# Download reprocessed counts (DLPFC)
COUNT_DLPFC_ID = 'syn8465067';
ALL_USED_IDs = COUNT_DLPFC_ID
COUNT = downloadFile(COUNT_DLPFC_ID) %>%
  as.data.frame()

@@

# Get ancestry vector calculated using gemtools
# ANCESTRY_ID = 'syn2511399'
# ALL_USED_IDs[length(ALL_USED_IDs)+1] = ANCESTRY_ID
# ANCESTRY = read.table(synGet(ANCESTRY_ID)@filePath, fill = T, header = T, sep = '\t') %>%
#   plyr::rename(c('DNA_report..Genotyping.Sample_ID' = 'GenotypingSampleID'))

# Get RNA qc metrics from synapse
METADATA_ALG_REP_DLPFC_ID = 'syn2279446'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_ALG_REP_DLPFC_ID
METADATA_ALG_REP_DLPFC = read.table(synGet(METADATA_ALG_REP_DLPFC_ID)@filePath, 
                                    fill = T, header = T, sep = ',') %>%
  dplyr::select(Sample.RNA.ID, Ribozero.Batch, Library.Batch, Flowcell.Batch) %>%
  dplyr::rename(SampleID = Sample.RNA.ID,
                LibraryBatch = Library.Batch, 
                RibozeroBatch = Ribozero.Batch, 
                FlowcellBatch = Flowcell.Batch) %>%
  unique()

# Get RNA qc metrics from synapse
METADATA_QC_DLPFC_ID = 'syn8539839'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_QC_DLPFC_ID
METADATA_QC = read.table(synGet(METADATA_QC_DLPFC_ID)@filePath, fill = T, header = T, sep = ',', row.names = 1) %>%
  dplyr::select(Sample, Total_Purity_Filtered_Reads_Sequenced, X5prime_Norm, Mean_Per_Base_Cov.,  
                Mean_CV, Fragment_Length_StdDev,  Mapped_Pairs, End_1_Mismatch_Rate, End_2_Mismatch_Rate,
                End_1_Mapping_Rate, End_2_Mapping_Rate, Mapped, Intragenic_Rate, Exonic_Rate, Intergenic_Rate,
                Intronic_Rate, rRNA_rate, Genes_Detected, Transcripts_Detected, Expression_Profiling_Efficiency,
                UNIQUE_READS._Uniquely_mapped_reads_percent) %>%
  dplyr::rename(SampleID = Sample, 
                IntragenicRate = Intragenic_Rate, 
                ExonicRate = Exonic_Rate, 
                IntronicRate = Intronic_Rate, 
                IntergenicRate = Intergenic_Rate, 
                GenesDetected = Genes_Detected, 
                TranscriptsDetected = Transcripts_Detected, 
                ExpProfEfficiency = Expression_Profiling_Efficiency, 
                rRNARate = rRNA_rate, 
                TotalReads = Total_Purity_Filtered_Reads_Sequenced, 
                PercentMapped = UNIQUE_READS._Uniquely_mapped_reads_percent)

# Get merged metadata
METADATA_ID = 'syn2299154'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_ID
METADATA = read.csv(synGet(METADATA_ID)@filePath, fill = T, header = T, check.names = F)

## Metadata with specific information for RNASeq processing
metadataVarOfInterest = c("Individual ID", "Institution", "Gender", "Age of Death", "PMI (in hours)", "Dx",

                          "DLPFC_RNA_isolation: Exclude?", "DLPFC_RNA_isolation: Sample RNA ID",
                          "DLPFC_RNA_isolation: RIN", "DLPFC_RNA_report: Exclude?")

# Filter metadata 
ind = colnames(METADATA) %in% metadataVarOfInterest
METADATA = METADATA[,ind]
colnames(METADATA) = gsub('[^[:alnum:]]','_',colnames(METADATA))

METADATA = METADATA %>%
  dplyr::select(Individual_ID, Institution, Gender, Age_of_Death, PMI__in_hours_, Dx, 
                DLPFC_RNA_isolation__Exclude_, DLPFC_RNA_isolation__Sample_RNA_ID, 
                DLPFC_RNA_isolation__RIN, DLPFC_RNA_report__Exclude_) %>%
  dplyr::rename(PMI = PMI__in_hours_, 
                IsolationExclude = DLPFC_RNA_isolation__Exclude_, 
                SampleID = DLPFC_RNA_isolation__Sample_RNA_ID, 
                RIN = DLPFC_RNA_isolation__RIN, 
                ReportExclude = DLPFC_RNA_report__Exclude_) %>%
  dplyr::filter(SampleID %in% colnames(COUNT)) %>%
  dplyr::mutate(Tissue = 'DLPFC') %>%
  list(.,METADATA_QC, METADATA_ALG_REP_DLPFC) %>%
  join_all %>% droplevels() %>%
  unique %>% as.data.frame()
METADATA$SampleID = as.character(METADATA$SampleID)

# Fix missing values
levels(METADATA$LibraryBatch)[1] = 'NotAvailable'
levels(METADATA$FlowcellBatch)[1] = 'NotAvailable'
levels(METADATA$RibozeroBatch)[1] = 'NotAvailable'
```

@@

writeLines('Following samples are marked exclude')
writeLines(paste(METADATA$SampleID[METADATA$IsolationExclude == 1 | METADATA$ReportExclude == 1], collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(IsolationExclude == 0, ReportExclude == 0)

@@

```{r gene.param}
## Get GC content from biomart
backgroundGenes = data.frame(ensembl_gene_id = rownames(COUNT))

@@

### Winsorise counts (Gene outliers in samples)
```{r winsorise.data}
LOG.CPM = cpm(PROCESSED_COUNTS$filteredExprMatrix$counts, log = T)

# Set gene counts in specific samples that are deviating 3 sd from other samples to 3SD limit
LOG.CPM = apply(LOG.CPM, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)

  x[x < (mn-3*std.dev)] = x[ind.low]
  x[x > (mn+3*std.dev)] = x[ind.high]
  return(x)
}) %>% t

# Back calculate counts for further analysis
LIB.SIZE = colSums(PROCESSED_COUNTS$filteredExprMatrix$counts)
NEW.COUNTS = (2^LOG.CPM) * t(replicate(dim(LOG.CPM)[1], LIB.SIZE))/1e6
```

### Library Normalisation
Initial library normalisation usign cqn
```{r cqn}
# Compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(NEW.COUNTS, 
                          x = GENE.GC.CONT[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gc_content'],
                          lengths = as.numeric(GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'Length']),
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset

@@

  x[x < (mn-3*std.dev)] = x[ind.low]
  x[x > (mn+3*std.dev)] = x[ind.high]
  return(x)
}) %>% t

@@

# Estimate voom weights
VOOM.GENE_EXPRESSION = limma::voom(NEW.COUNTS, design = DESIGN)
VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E

@@

# Estimate voom weights
VOOM.GENE_EXPRESSION1 = limma::voom(NEW.COUNTS, design = DESIGN1)
VOOM.GENE_EXPRESSION1$E = CQN.GENE_EXPRESSION$E

@@

# Estimate voom weights
VOOM.GENE_EXPRESSION2 = voom(NEW.COUNTS, design = DESIGN2)
VOOM.GENE_EXPRESSION2$E = CQN.GENE_EXPRESSION$E

@@

# Download all related genesets from synapse
geneset.files = synQuery('select * from file where parentId == "syn3240583"')
ALL_USED_IDs = c(ALL_USED_IDs, geneset.files$file.id)
genesets.to.test = sapply(geneset.files$file.name, function(dataSource, geneset.files){
  tmp = downloadFile(geneset.files$file.id[geneset.files$file.name == dataSource]) %>%
    dlply(.(Name), .fun = function(x){
      str_split(x$symBeforeOverlap, '\\|') %>% unlist %>% unique
    })
  }, geneset.files) %>%
  CovariateAnalysis::filterGeneSets(backgroundGenes) %>%
  do.call(c,.)

@@

# Code
CODE <- Folder(name = "HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN (Model Selection)", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'CMC_ACC_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = File('CMC_ACC_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
annotations(COV_OBJ) = annotations(CODE)
annotations(COV_OBJ)$dataSubType = 'covariates'
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)

# Store filtered counts
NEW.COUNTS %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('CMC_ACC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
annotations(COUNT_OBJ) = annotations(CODE)
annotations(COUNT_OBJ)$dataSubType = 'filteredCounts'
COUNT_OBJ = synStore(COUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store logCPM
CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('CMC_ACC_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
annotations(LCOUNT_OBJ) = annotations(CODE)
annotations(LCOUNT_OBJ)$dataSubType = 'filteredLCPM'
LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_offset.tsv', sep = '\t', row.names=F, quote=F)
OFFSET_OBJ = File('CMC_ACC_DLPFC_offset.tsv', name = 'Gene length and GC content offset', parentId = CODE$properties$id)
annotations(OFFSET_OBJ) = annotations(CODE)
annotations(OFFSET_OBJ)$dataSubType = 'offset'
OFFSET_OBJ = synStore(OFFSET_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store design matrix
DM1$design %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'CMC_ACC_DLPFC_Design.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = File('CMC_ACC_DLPFC_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
annotations(DM_OBJ) = annotations(CODE)
annotations(DM_OBJ)$dataSubType = 'designMatrix'
DM_OBJ = synStore(DM_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store residual gene expression for network analysis
RESIDUAL.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_ACC_DLPFC_netResidualExpression.tsv', 
                name = 'Normalised, covariates removed residual expression (for network analysis)', 
                parentId = CODE$properties$id)
annotations(nEXP_OBJ) = annotations(CODE)
annotations(nEXP_OBJ)$dataSubType = 'residualGeneExpForNetAnlz'
nEXP_OBJ = synStore(nEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store differential expression results
write.table(DE, file = 'CMC_ACC_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('CMC_ACC_DLPFC_DiffExpression.tsv', 
                name = 'Differential Expression Results (Dx.Tissue)', 
                parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store enrichment results
write.table(enrichment.results, file = 'CMC_ACC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_ACC_DLPFC_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
annotations(ENRICH_OBJ) = annotations(CODE)
annotations(ENRICH_OBJ)$dataSubType = 'enrichResults'
ENRICH_OBJ = synStore(ENRICH_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
|  Enrichment Analysis                        |  `r ENRICH_OBJ$properties$id`    |

>>>>

knit2synapse::knitToFolderEntity(file = "./HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd",
                                 parentId ="syn9846623",
                                 folderName = 'HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN (Model Selection)')
```

@@

## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)

library(limma)
library(psych)
library(edgeR)
library(cqn)
library(lme4)
library(biomaRt)

@@

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='CMC')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id, sep){
  tmp = data.table::fread(synGet(id)@filePath,  data.table = F, header = T, sep = sep)
}

# Download reprocessed counts (DLPFC)
COUNT = downloadFile('syn8465067', sep = '\t') %>%
  as.data.frame()
ALL_USED_IDs = 'syn8465067'

@@

# Get clinical metadata
METADATA_CLINICAL = downloadFile('syn2279441', sep = ',') %>%
  dplyr::rename(Individual_ID = `Individual ID`)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn2279441')

# Get RNA alignment report from synapse
METADATA_ALG_REP_DLPFC = downloadFile('syn2279446', sep = ',') %>%
  dplyr::select(`Exclude?`, `Sample RNA ID`, `Ribozero Batch`, `Library Batch`, `Flowcell Batch`) %>%
  dplyr::rename(Exclude = `Exclude?`,
                SampleID = `Sample RNA ID`,
                LibraryBatch = `Library Batch`, 
                RibozeroBatch = `Ribozero Batch`, 
                FlowcellBatch = `Flowcell Batch`) %>%
  distinct()
ALL_USED_IDs = c(ALL_USED_IDs, 'syn2279446')

# Get RNA qc metrics from synapse
METADATA_RNASEQ_QC = downloadFile('syn8539839', sep = ',') %>%
  dplyr::select(V1, Sample, Total_Purity_Filtered_Reads_Sequenced, X5prime_Norm, Mean_Per_Base_Cov.,  
                Mean_CV, Fragment_Length_StdDev,  Mapped_Pairs, End_1_Mismatch_Rate, End_2_Mismatch_Rate,
                End_1_Mapping_Rate, End_2_Mapping_Rate, Mapped, Intragenic_Rate, Exonic_Rate, Intergenic_Rate,
                Intronic_Rate, rRNA_rate, Genes_Detected, Transcripts_Detected, Expression_Profiling_Efficiency,
                UNIQUE_READS._Uniquely_mapped_reads_percent) %>%
  dplyr::rename(SampleID = Sample, 
                IntragenicRate = Intragenic_Rate, 
                ExonicRate = Exonic_Rate, 
                IntronicRate = Intronic_Rate, 
                IntergenicRate = Intergenic_Rate, 
                GenesDetected = Genes_Detected, 
                TranscriptsDetected = Transcripts_Detected, 
                ExpProfEfficiency = Expression_Profiling_Efficiency, 
                rRNARate = rRNA_rate, 
                TotalReads = Total_Purity_Filtered_Reads_Sequenced, 
                PercentMapped = UNIQUE_READS._Uniquely_mapped_reads_percent)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn8539839')

# Get RNASeq isolation report
METADATA_RNA_ISOLATION = downloadFile('syn2279445', sep = ',') %>%
  dplyr::select(`Sample RNA ID`, RIN) %>%
  dplyr::rename(SampleID = `Sample RNA ID`)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn2279445')

# Get individual id mapping
METADATA_IID = downloadFile('syn12979139', sep = '\t') %>%
  dplyr::select(Data_ID, IID_SAMPLE, label) %>%
  dplyr::rename(Individual_ID = IID_SAMPLE,
                SampleID = Data_ID) %>%
  distinct()
ALL_USED_IDs = c(ALL_USED_IDs, 'syn12979139')

# Merge metadata
METADATA = dplyr::inner_join(METADATA_ALG_REP_DLPFC, METADATA_RNASEQ_QC) %>%
  dplyr::inner_join(METADATA_IID) %>%
  dplyr::inner_join(METADATA_CLINICAL) %>%
  dplyr::inner_join(METADATA_RNA_ISOLATION) %>%
  dplyr::select(SampleID, Individual_ID, label, 
                LibraryBatch, RibozeroBatch, FlowcellBatch,
                Dx, Gender, `PMI (in hours)`, `Age of Death`, RIN,
                TotalReads, X5prime_Norm, Mean_Per_Base_Cov.,
                Mean_CV, Fragment_Length_StdDev, Mapped_Pairs, End_1_Mismatch_Rate, End_2_Mismatch_Rate, 
                Mapped, IntragenicRate, ExonicRate, IntergenicRate, IntronicRate, rRNARate, GenesDetected,
                TranscriptsDetected, ExpProfEfficiency, PercentMapped) %>%
  dplyr::rename(PMI = `PMI (in hours)`,
                Age_of_Death = `Age of Death`) %>%
  dplyr::mutate_at(.vars = c('LibraryBatch', 'RibozeroBatch', 'FlowcellBatch', 'Dx', 'Gender'), 
                   .funs = function(x){
                     x = forcats::fct_explicit_na(x, na_level = 'NotAvailable')
                     levels(x)[levels(x) == ''] = 'NotAvailable'
                     return(x)
                   }) %>%
  dplyr::mutate(Tissue = 'DLPFC')
```

@@

writeLines('Following samples are marked exclude')
writeLines(paste(METADATA$SampleID[METADATA$label == 'exclude'], collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(label == 'accept')

@@

```{r gene.param, include = FALSE}
## Get GC content from biomart
backgroundGenes = data.frame(ensembl_gene_id = rownames(COUNT))

@@

### Library Normalisation and Winsorise data
Initial library normalisation usign cqn and setting gene outliers to NA
```{r cqn}
# Compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(PROCESSED_COUNTS$filteredExprMatrix$counts, 
                          x = GENE.GC.CONT[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gc_content'],
                          lengths = as.numeric(GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'Length']),
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset

@@

  x[x < (mn-3*std.dev)] = NA
  x[x > (mn+3*std.dev)] = NA
  return(x)
}) %>% t

@@

# Estimate voom weights
tmp = NEW.COUNTS
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION = limma::voom(tmp, design = DESIGN)
VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E

@@

# Estimate voom weights
tmp = NEW.COUNTS
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION1 = limma::voom(tmp, design = DESIGN1)
VOOM.GENE_EXPRESSION1$E = CQN.GENE_EXPRESSION$E

@@

# Estimate voom weights
tmp = NEW.COUNTS
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION2 = voom(tmp, design = DESIGN2)
VOOM.GENE_EXPRESSION2$E = CQN.GENE_EXPRESSION$E

@@

# Download all related genesets from synapse
synapseClient::synapseLogin()
geneset.files = synapseClient::synQuery('select * from file where parentId == "syn3240583"')
ALL_USED_IDs = c(ALL_USED_IDs, geneset.files$file.id)
genesets.to.test = sapply(geneset.files$file.name, function(dataSource, geneset.files){
  tmp = downloadFile(geneset.files$file.id[geneset.files$file.name == dataSource], sep = '\t') %>%
    dlply(.(Name), .fun = function(x){
      str_split(x$symBeforeOverlap, '\\|') %>% unlist %>% unique
    })
}, geneset.files) %>%
  CovariateAnalysis::filterGeneSets(backgroundGenes) %>%
  do.call(c,.)

@@

# Code
CODE <- synapseClient::Folder("HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN (Model Selection)", 
                              parentId = parentId)
synapseClient::synSetAnnotations(CODE, annotations = all.annotations)
CODE <- synapseClient::synStore(CODE)

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'CMC_ACC_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = synapseClient::File('CMC_ACC_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
synapseClient::annotations(COV_OBJ) = synapseClient::annotations(CODE)
synapseClient::annotations(COV_OBJ)$dataSubType = 'covariates'
COV_OBJ = synapseClient::synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                                  executed = thisFile, activityDescription = activityDescription)

# Store filtered counts
NEW.COUNTS %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = synapseClient::File('CMC_ACC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
synapseClient::annotations(COUNT_OBJ) = synapseClient::annotations(CODE)
synapseClient::annotations(COUNT_OBJ)$dataSubType = 'filteredCounts'
COUNT_OBJ = synapseClient::synStore(COUNT_OBJ, activity = synapseClient::synGetActivity(COV_OBJ$properties$id))

# Store logCPM
CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = synapseClient::File('CMC_ACC_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
synapseClient::annotations(LCOUNT_OBJ) = synapseClient::annotations(CODE)
synapseClient::annotations(LCOUNT_OBJ)$dataSubType = 'filteredLCPM'
LCOUNT_OBJ = synapseClient::synStore(LCOUNT_OBJ, activity = synapseClient::synGetActivity(COV_OBJ$properties$id))

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_offset.tsv', sep = '\t', row.names=F, quote=F)
OFFSET_OBJ = synapseClient::File('CMC_ACC_DLPFC_offset.tsv', name = 'Gene length and GC content offset', parentId = CODE$properties$id)
synapseClient::annotations(OFFSET_OBJ) = synapseClient::annotations(CODE)
synapseClient::annotations(OFFSET_OBJ)$dataSubType = 'offset'
OFFSET_OBJ = synapseClient::synStore(OFFSET_OBJ, activity = synapseClient::synGetActivity(COV_OBJ$properties$id))

# Store design matrix
DM1$design %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'CMC_ACC_DLPFC_Design.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = synapseClient::File('CMC_ACC_DLPFC_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
synapseClient::annotations(DM_OBJ) = synapseClient::annotations(CODE)
synapseClient::annotations(DM_OBJ)$dataSubType = 'designMatrix'
DM_OBJ = synapseClient::synStore(DM_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store residual gene expression for network analysis
RESIDUAL.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = synapseClient::File('CMC_ACC_DLPFC_netResidualExpression.tsv', 
                               name = 'Normalised, covariates removed residual expression (for network analysis)', 
                               parentId = CODE$properties$id)
synapseClient::annotations(nEXP_OBJ) = synapseClient::annotations(CODE)
synapseClient::annotations(nEXP_OBJ)$dataSubType = 'residualGeneExpForNetAnlz'
nEXP_OBJ = synapseClient::synStore(nEXP_OBJ, activity = synapseClient::synGetActivity(COV_OBJ$properties$id))

# Store differential expression results
write.table(DE, file = 'CMC_ACC_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = synapseClient::File('CMC_ACC_DLPFC_DiffExpression.tsv', 
                               name = 'Differential Expression Results (Dx.Tissue)', 
                               parentId = CODE$properties$id)
synapseClient::annotations(DEXP_OBJ) = synapseClient::annotations(CODE)
synapseClient::annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synapseClient::synStore(DEXP_OBJ, activity = synapseClient::synGetActivity(COV_OBJ$properties$id))

# Store enrichment results
write.table(enrichment.results, file = 'CMC_ACC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = synapseClient::File('CMC_ACC_DLPFC_EnrichResults.tsv', 
                                 name = 'Enrichment Analysis Results (Dx.Tissue)', 
                                 parentId = CODE$properties$id)
synapseClient::annotations(ENRICH_OBJ) = synapseClient::annotations(CODE)
synapseClient::annotations(ENRICH_OBJ)$dataSubType = 'enrichResults'
ENRICH_OBJ = synapseClient::synStore(ENRICH_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
|  Enrichment Analysis                        |  `r ENRICH_OBJ$properties$id`    |
